Quality assurance of digital twins: An experience report in the automotive industry

### 2023-09-18 manuscripts/quatic-2023/main.tex
start working on second paper

    The first serious discussions of subcategorization of quality trace back to the beginning of the 20th century with the emergence of product-focused quality management practices in manufacturing~\cite{HistoryofControlEngineering}.
    Later on, with the development of new technologies, subcategorization of quality was evolved and extended to other areas, such as software, which appeared in the 1970s~\cite{ThePsychologyofComputerProgramming}.
    With this emergence, assessing the software quality became inevitable and as a result, a considerable amount of software quality models and characteristics have been established~\cite{SoftwareQualityModels,Charecteristicsofsoftwarequality,AnActivityBasedQualityModelforMaintainability}.
    As an example, ISO/IEC:25010 has standardized eight software quality characteristics, including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, 
    and portability, to determine software quality~\cite{ISO/IEC:25010}.

>>>>

    The first serious discussions of subcategorization of quality trace back to the beginning of the 20th 
    century with the emergence of product-focused quality management practices in manufacturing~\cite{HistoryofControlEngineering}.
    Later on, with the development of new technologies, 
    subcategorization of quality was evolved and extended to other areas, 
    such as software, which appeared in the 1970s~\cite{ThePsychologyofComputerProgramming}.
    With this emergence, assessing the software quality became inevitable 
    and as a result, a considerable amount of software quality models and 
    characteristics have been established~\cite{SoftwareQualityModels,Charecteristicsofsoftwarequality,
    AnActivityBasedQualityModelforMaintainability}.
    As an example, ISO/IEC:25010 has standardized eight software quality characteristics, 
    including functional suitability, performance efficiency, compatibility, usability, 
    reliability, security, maintainability, 
    and portability, to determine software quality~\cite{ISO/IEC:25010}.
